Estimation of cloud-corrected microwave humidity radiances with associated uncertainties

### 2020-10-31 Article/ici_submm_cloudcorr.tex
some editing, and added table with SI and Buehler_etal filtering

%\documentclass[amt, manuscript]{copernicus}
\documentclass[amt]{copernicus}

@@

In this study, we present methodology to identify and correct the cloud impact in microwave humidity radiances. A channel specific quantile regression(QRNN) based approach is formulated to estimate the posterior distributions of noise free clear sky (NFCS) radiances. The applicability of the approach is demonstrated by application to current sensor MWHS-2. With the future outlook, the applicability to sub-millimeter (sub-mm) channels is also investigated. The results are compared against the NFCS simulations. With the present sensors, the approach is only partially successful in removing the cloud contamination. Though most of the cases with high cloud impact are corrected, cases with low cloud impact are only partially corrected. This is comparable/better to the level of accuracy achieved with operational cloud-filtering techniques, like scattering index. However with sub-mm channels, we are able to successfully correct most of the cases with cloud impact. The resulting error distributions are symmetric with very low spread. The methodology also works well even when only one of the higher frequencies is available. In some cases, the combination of 183\,GHz and sub-mm channels also results in a lower variability than noise.  Another advantage of using QRNN is that predicted quantiles can be employed to quantify the case-specific uncertainty estimates. The results show that QRNN is successful in representing the uncertainty for most of the scenes individually. Despite individual variations for each channel, it is observed that uncertainty consistently increases with the error in the performance.

\todo {write one line, why important for DA}

@@

\section{Data and methods}
%
\subsection{Satellite Instruments}
%
\subsubsection{ MicroWave Humidity Sounder 2}
%
%t
\begin{table}[t]
	\caption{Specifications of MWHS-2 channels relevant to this study.}
	\label{tab:specifications_MWHS2}	
	\begin{tabular}{crrr}
		\tophline
		Channel & Frequency 	& Bandwidth & NE$\Delta$T \\
		& [GHz]			& [MHz]		& [K]		\\
		\middlehline
		1	&	89.0   		  & 1500			&	1.0	\\
		6	&	118.75±1.1    & \phantom{0}200 	&	1.6\\
		7	&	118.75±2.5    & \phantom{0}200 	&	1.6\\
		10	&	150.0         & 1500 			&	1.0 \\
		11	&	183.31±1      & \phantom{0}500  &	1.0 \\
		12  & 	183.31±1.8    & \phantom{0}700 	&   1.0\\
		13  & 	183.31±3      & 1000    		&	1.0	\\
		14  & 	183.31±4.5    & 2000    		&	1.0\\
		15  & 	183.31±7      & 2000  			&	1.0  \\
		\bottomhline
	\end{tabular}
	\belowtable{} % Table Footnotes
\end{table}
MicroWave Humidity Sounder 2 (MWHS-2) is an instrument onboard FengYun-3C (FY-3C). MWHS-2 is designed to observe the distribution of global atmospheric thermodynamics information, and monitor the severe convective systems. It is a cross track scanning microwave radiometer and measures 15 frequencies in the range 89-191\,GHz. 89\,GHz and 150\,GHz are window channels, five humidity sounding channels are centered at 183.31\,GHz and eight temperature sounding channels centered at 118.75\,GHz oxygen absorption line. The five humidity sounding channels are similar to MWS (Micro Wave Sounder) and ATMS (Advanced Technology Microwave Sounder). As of December 2019, observations from MWHS-2 are routinely assimilated at ECMWF \citep{duncan2020MWHS}. The channels relevant to this study are described on Table~\ref{tab:specifications_MWHS2}.

@@

Ice Cloud Imager (ICI) is a new instrument on board EPS-SG(EUMETSAT Polar System - Second Generation) satellite Metop-SG. Metop-SG is scheduled for launch in 2023, and it will make ICI the first operational sensor observing Earth using sub-millimeter(sub-mm) wavelengths. The main objective of ICI is to use high frequency channels for measuring ice cloud properties and improve the representation of ice clouds in regional and global Numerical Weather Prediction(NWP) models. ICI is a conically scanning radiometer that will measure 13 frequencies from 183 GHz up to 664 GHz.  ICI consists of channels receiving frequencies around 183.31\,GHz, 325.15\,GHz and 448.00\,GHz, measuring vertical polarization. While other channels around frequencies 243.20\,GHz and 664.00\,GHz are ``window channels'' and measure both vertical and horizontal polarization. The instrument will observe earth from a mean altitude of 832\,Km with sensor viewing angle 44.767$^\circ$(measured from nadir). For all the channels, the mean footprint size is about 15\,Km, but the exact geo-location of samples differs. Therefore a simultaneous utilization of data from different channels requires remapping to a common footprint \citep{eriksson:towar:20}.

@@

\subsection{Simulations}
%
MWHS-2 simulated radiances are routinely calculated at ECMWF for their use in the ECMWF assimilation system. RTTOV and RTTOV-SCATT are used to calculate the radiances in the clear-sky and all-sky conditions respectively. For this study, MWHS-2 brightness temperatures for the period June-July 2020 were used. Out of all the available observations, we extracted data for latitudinal range $60^{\degree}$\,S to $60^{\degree}$\,N and satellite zenith angle less than $7.5^{\degree}$. With this filter we had 340\,000 cases for each frequency.

ICI, AWS frequencies were simulated with ARTS. Cloudsat profiles during August 2015 were randomly selected for forward simulations. The input data were restricted between $60^{\degree}$S to $60^{\degree}$N, and surface was below 500\,m. Both clear-sky and all-sky scenarios were simulated. The complete simulation setup is described in Appendix \ref{appendix:ARTS_setup}. For each ICI frequency in Table~\ref{tab:ICI_MWI_channels}, 220\,000 cases were simulated. For both instruments, the channel frequencies were simulated directly. For AWS, 140\,000 cases were simulated. Forward simulations were performed for 21 monochromatic frequencies. These frequencies were interpolated to a finer grid to get the AWS channel brightness temperatures. All AWS sensor viewing angles (from $0^\circ$ to $45^\circ$) were simulated, but the results described in this study are based on nadir viewing angle.

All simulations were noise free, so to incorporate the measurement uncertainties, whenever needed, gaussian noise was added to according to the channel NE$\Delta$T (Table~\ref{tab:specifications_MWHS2} - Table~\ref{tab:specifications_AWS}).

The noise free simulations were split into training and testing datasets. The training dataset was used to train the machine learning model, while the testing dataset was used to evaluate the trained model. The construction and details of the model are described in Sect.~\ref{sec:QRNN}. For MWHS-2, 220\,000 simulations were randomly selected as training dataset, while 70\,000 were used for testing. For ICI, 175\,000 cases were randomly picked to form the training set. The remaining 45\,000 were used for testing. A smaller database was selected for AWS. 120\,000 simulations were used for training and the rest were used for testing.

@@

For this application, the predicted percentiles are chosen to be
$0.2\%, 3\%, 16\%, 50\%, 85\%, 97\%$ and $99.8\%$. For a Gaussian
distribution with mean $\mu$ and standard deviation $\sigma$ the
approximately corresponds to $\mu -3\sigma, \mu-2\sigma, \mu-\sigma
, \mu, \mu + \sigma, \mu + 2\sigma, \mu + 3\sigma$ and thus allows
estimating the $\pm 1, \pm 2$ and $\pm 3\sigma$ confidence intervals.
The median is used as point estimate for the corrected $\ynfcs$.

QRNN's are trained to minimize the mean of the quantile loss functions
%
\begin{align}
  \mathcal{L}_\tau(y_\tau, y) &=
  \begin{cases}
    \tau|y - y_\tau|, & y_\tau < y \\ (1 - \tau)|y_\tau - y|, & \text{otherwise}
    \\
  \end{cases}
\end{align}
%
for all predicted quantile fractions $\tau$, where $\y_\tau$ is the predicted
quantile and $y$ the reference value from the training set. The quantile loss is
used in this study as a performance criterion for the tuning of the hyper
parameters of the QRNN. In addition to the quantile loss, also the Continuously
Ranked Probability Score (CRPS) is considered. Given a predicted cumulative
distribution function (CDF) $F$ and the reference value $y$, the CRPS is defined as
%
\begin{align}
  \text{CRPS}(F, y) = \int_{-\infty}^{\infty} \left (F(y') - y\right )^2\: dy'.
\end{align}
%
To compute the CRPS for a predictions from a QRNN, the predicted quantiles are
used to derive a piece-wise linear approximation of the CDF of the predicted
distribution and evaluate the above integral.

The implementation of QRNN is similar to one described in \citet{pfreundschuh:aneur:18}, except that instead of Kera python package, PyTorch, an open source machine learning
library \citep{paszke2017automatic} is used. This version is developed and available as a part of \textit{typhon:tools for atmospheric research} software package [\todo{developer's version??}]. The major challenge for implementing QRNN for the current application was to select high performing neural network architecture. This was obtained through grid search over different hyperparameter configurations. The details are described in Appendix~\ref{appendix:hyperparamter}

\subsubsection{QRNN model configurations}
%
In the study, two QRNN configurations are formulated for cloud-correction. The basic construction of both is to train for each of the available 183\,GHz channels individually, using certain input training data. The input data is all-sky brightness temperatures from selected input channels and/or additional data like land/sea mask. The selection of input channels is sensor dependent and is described in detail when introduced. The output in both configurations is NFCS value for the target 183\,GHz channel. The two configurations differ only by the number of input 183\,GHz channels used in the training process:

\begin{enumerate}
	\item QRNN-single: In this configuration, the training input includes all-sky brightness temperatures from the target 183\,GHz channel and other non-humidity channels along with additional data, if relevant. No other 183\,GHz channel is included.

@@

For all three sensors described in this study, one or both of the above QRNN configurations are used.

\subsection{Evaluation metrics}
\label{sec:validation}
\begin{figure}[t]
	\centering
	\includegraphics[height=45mm]{Figures/posterior_distribution_I1V.pdf} 
	\caption{An example showing the predicted quantiles of the conditional distribution of $\ynfcs$ }
	\label{fig:posterior_distribution_I1V}	
\end{figure}
QRNN predictions are posterior probability distribution of the NFCS values described over the selected quantiles. This is contrast with other conventional correction/filtering methods. In order to facilitate the interpretation of results, an example QRNN output is shown in Fig.~\ref{fig:posterior_distribution_I1V}. This examples illustrate the predicted quantiles for three different cases. For most analysis, usually a single point estimate is required. In Bayesian analysis, usually the posterior mean or posterior median are selected as point estimates. In this study, we assume the posterior median to be the best estimate for the predicted NFCS value ($\ynfcs$). To analyse the ability of QRNN in correctly predicting the point estimate, deviations of point estimates from the corresponding true value ($\yonfcs$) are evaluated using common performance indicators like bias, mean absolute error(MAE) and standard deviation (STD). The asymmetry of error distributions around their mean is also calculated through the measure of skewness. Fisher-Pearson coefficient of skewness is used to calculate the measure of skewness: 
\begin{equation}
g_1 = \frac{m_3}{m_2^{3/2}}, 
\end{equation}
where $m_2$ and $m_3$ are biased sample's second and third central moments.

For probabilistic predictions, accuracy of the point estimate is inadequate to gauge the complete performance. In a successful QRNN training, QRNN learns to predict not only an accurate point estimate but also correct underlying uncertainty. An ideal QRNN output should be sharp or in other words, concentrated in the vicinity of the point estimate. The predicted posterior distribution should also be well calibrated, that is, reflect the true probability distribution. A straightforward way to compare the two distribution is to plot the frequency of predictions and frequency of the true value in different prediction intervals. This is also commonly known as calibration plot. In a well-calibrated QRNN prediction, the calibration plot should follow the straight line y = x. Another way to assess how well the predicted posterior distribution reflects the observed errors is to compare predicted and observed errors. The predicted error is deviation of a random sample drawn from the posterior distribution to its median. In this study, we use both calibration plot and predicted errors to assess the correctness of predicted uncertainties.

@@

\section{Correcting cloud affected data in MWHS-2}
%
In this section, we introduce the QRNN based cloud  correction in the context of current operational sensors.  We use MWHS-2 to demonstrate the results. The choice is motivated by the fact that MWHS-2 has five complementary 183\,GHz channels as ATMS/MWS, along with additional 118\,GHz channel. In order to test the correction approach multiple QRNN experiments are performed and the results are compared for MWHS-2 channel 14. Later the methodology is expanded to other channels.  Further, the estimates of case-specific uncertainties obtained from QRNN are also evaluated.

\subsection{Experiments}
%
For MWHS-2, multiple experiments using both QRNN configurations are performed. The aim of the experiments is to delve into the sensitivity of the cloud correction to different input channels:

@@

	\item In the first experiment, we examine the performance of QRNN cloud correction with MWHS-2 window channels: 89 and 150\,GHz. In ECMWF NWP system, the differences between the observations of these two window channels (Scattering Index) \citep{Lu2015FY3C} are used to identify the cloud affected data for ATMS, MHS and MWHS-2. To investigate the potential impact of window channels in QRNN based cloud correction, the configuration QRNN-single is applied to predict cloud free radiances. In this experiment, the training input includes all-sky brightness temperatures from target 183\,GHz channel, 89\,GHz and 150\,GHz. Both 89 and 150\,GHz are window channels so the land sea mask is also included as a training input. For example for channel 14, the training inputs are all-sky brightness temperatures from channels 14, 1, 10 and land/sea mask. This combination is referred as 89+150\,GHz in the text.

@@

	\item The third experiment is designed to assess the exclusive impact of 150\,GHz in cloud correction. In this experiment, QRNN-single is trained with brightness temperatures from 150\,GHz along with the target channel and land/sea mask.

	\item The fourth experiment is based on the configuration QRNN-all. In this experiment, we use 89 and 150\,GHz channels along with all 183\,GHz channels to train QRNN. This experiment is motivated by the fact that in all-sky conditions, brightness temperatures between outer and inner humidity channels can be used as a criterion for cloud filtering\cite{buehler:aclou:07}. With QRNN-all, we investigate if additional humidity channels in the training process can improve the performance by providing auxiliary information. It should be noted that though the training inputs are same for each 183\,GHz channel, the output is the target 183\,GHz channel; thus each channel still needs to be trained separately. Land/sea mask is also included in the training. This combination is denoted as 89+150+183\,GHz
\end{enumerate}

@@

\subsubsection{QRNN-single applied to MWHS-2 channel 14} 
\begin{figure}[t]
	\centering
	\includegraphics[height=55mm]{Figures/QRNN_output_mwhs.pdf} 
	\caption{Distributions of point estimate $\ynfcs$ obtained from QRNN-single 89+150\,GHz for MWHS-2 channel 14. The corresponding distribution for all-sky and clear-sky simulations are also shown.}
	\label{fig:distribution_predicted_mwhs14}	
\end{figure}
\begin{table*}[t]
	\caption{Error statistics for deviations of MWHS-2 NFSC predictions to simulations. Results are for different QRNN experiments for MWHS-2 channel 14. With configuration QRNN-single, the results are from combinations 89+150\,GHz, 89+150+118\,GHz and 150\,GHz. While with QRNN-all, only combination 89+150+183\,GHz is shown. The statistics for uncorrected all-sky simulations and NFCS simulations are also provided. The label ``All'' refers to entire predicted dataset, while Filtered(5\,K) denotes the subset where predictions with correction greater than 5\,K are omitted. The fraction of rejected cases is given in parentheses. }
	\label{tab:error_statistics_mwhs_14}
	\begin{tabular}{lrr|rr|rr|rr|rr}
		\tophline
		&\multicolumn{2}{c|}{Simulations}& \multicolumn{6}{c|}{QRNN-single} & \multicolumn{2}{c}{QRNN-all}\\
		\cline{2-11}
		%		\hline
		&   Clear-sky &   All-sky &  \multicolumn{2}{c|}{89+150\,GHz} & \multicolumn{2}{c|}{89+150+118\,GHz} & \multicolumn{2}{c|}{150\,GHz} & \multicolumn{2}{c}{89+150+183\,GHz}\\
		&			   &			& All & Filtered(5K) & All & Filtered(5K) & All & Filtered(5K)  & All & Filtered(5K)\\
		\middlehline
		bias     &  0.00 &  -0.84 & -0.09 & -0.08(3.3\%) & -0.04 & -0.03(3.4\%) & -0.09 & -0.09(3.2\%) & -0.09(3.3\%) & -0.08(3.3\%)  \\
		mae      &  0.80 &   1.45 &  0.88 &  0.86 &  0.89 &  0.87 &  0.89 &  0.87 &  0.62 &  0.59\\
		std      &  1.00 &   3.90 &  1.19 &  1.14 &  1.19 &  1.15 &  1.21 &  1.16 &  0.90 &  0.83\\
		skewness & -0.00 & -14.34 & -1.11 & -0.93 & -1.00 & -0.84 & -0.88 & -0.98 & -1.58 & -1.62\\
		\bottomhline
	\end{tabular}
\end{table*}
Fig.~\ref{fig:distribution_predicted_mwhs14} shows the distribution of QRNN predictions obtained from QRNN. QRNN predictions are able to remove the extended mass concentration to the left is due hydrometeor impact, and overall a good match with the NFCS simulations is observed. QRNN is unable to predict the lowest clear-sky brightness temperatures, but cases with brightness temperatures around 260\,K occur frequently.  Table~\ref{tab:error_statistics_mwhs_14} shows the error statistics for the predictions shown in Fig.~\ref{fig:distribution_predicted_mwhs14}. In the uncorrected data, cloud impact causes a large negative skewness(-14.34) in the error distribution and the corresponding bias is -0.84\,K. Training QRNN with 89 and 150\,GHz removes a part of the cloud impact and reduces the bias to -0.09\,K, and the skewness is -1.11. The MAE and STD are also reduced after correction, but are higher than noise. Including 118\,GHz in the training, gives comparable results as 89+150\,GHz. With 118\,GHz, the error distributions have lower bias and are more symmetric, but the MAE and STD remain unaltered. This indicates that the information from 118\,GHz channels can be beneficial in predicting few cases correctly, but the overall consequence is not exceptionally different from 89+150\,GHz. Similar is the case with using only 150\,GHz. In the latter, predictions have the most symmetric  error distributions, but the highest spread.

>>>>

\documentclass[amt, manuscript]{copernicus}
%\documentclass[amt]{copernicus}

@@

In this study, we present methodology to identify and correct the cloud impact in microwave humidity radiances. A channel specific quantile regression(QRNN) based approach is formulated to estimate the posterior distributions of noise free clear sky (NFCS) radiances. The applicability of the approach is demonstrated by application to current sensor MWHS-2. With the future outlook, the applicability to sub-millimeter (sub-mm) channels is also investigated. The results are compared against the NFCS simulations. With the present sensors, the approach is only partially successful in removing the cloud contamination. Though most of the cases with high cloud impact are corrected, cases with low cloud impact are only partially corrected. This is comparable/better to the level of accuracy achieved with operational cloud-filtering techniques, like scattering index. However with sub-mm channels, we are able to successfully correct most of the cases with cloud impact. The resulting error distributions are symmetric with very low spread. The methodology also works well even when only one of the higher frequencies is available. In some cases, the combination of 183\,GHz and sub-mm channels also results in a lower variability than noise.  Another advantage of using QRNN is that predicted quantiles can be employed to quantify the case-specific uncertainty estimates. The results show that QRNN is successful in representing the uncertainty for most of the scenes individually. Despite individual variations for each channel, it is observed that uncertainty consistently increases with the error in the performance. From data assimilation perspective, high quality cloud cleared radiances with symmetric error distribution and case-specific uncertainties are extremely valuable.

@@

\section{Data and methods}
%
\subsection{Satellite Instruments}
%
\subsubsection{ MicroWave Humidity Sounder 2}
%
%t
\begin{table}[t]
	\caption{Specifications of MWHS-2 channels relevant to this study.}
	\label{tab:specifications_MWHS2}	
	\begin{tabular}{crrr}
		\tophline
		Channel & Frequency 	& Bandwidth & NE$\Delta$T \\
		& [GHz]			& [MHz]		& [K]		\\
		\middlehline
		1	&	89.0   		  & 1500			&	1.0	\\
		6	&	118.75±1.1    & \phantom{0}200 	&	1.6\\
		7	&	118.75±2.5    & \phantom{0}200 	&	1.6\\
		10	&	150.0         & 1500 			&	1.0 \\
		11	&	183.31±1      & \phantom{0}500  &	1.0 \\
		12  & 	183.31±1.8    & \phantom{0}700 	&   1.0\\
		13  & 	183.31±3      & 1000    		&	1.0	\\
		14  & 	183.31±4.5    & 2000    		&	1.0\\
		15  & 	183.31±7      & 2000  			&	1.0  \\
		\bottomhline
	\end{tabular}
	\belowtable{} % Table Footnotes
\end{table}
MicroWave Humidity Sounder 2 (MWHS-2) is an instrument onboard FengYun-3C (FY-3C). MWHS-2 is designed to observe the distribution of global atmospheric thermodynamics information, and monitor the severe convective systems. It is a cross track scanning microwave radiometer and measures 15 frequencies in the range 89-191\,GHz. 89\,GHz and 150\,GHz are window channels, five humidity sounding channels are centered at 183.31\,GHz and eight temperature sounding channels are centered at 118.75\,GHz oxygen absorption line. The five humidity sounding channels are similar to MWS (Micro Wave Sounder) and ATMS (Advanced Technology Microwave Sounder). As of December 2019, observations from MWHS-2 are routinely assimilated at ECMWF \citep{duncan2020MWHS}. The channels relevant to this study are described on Table~\ref{tab:specifications_MWHS2}.

@@

Ice Cloud Imager (ICI) is a new instrument on board EPS-SG(EUMETSAT Polar System - Second Generation) satellite Metop-SG. Metop-SG is scheduled for launch in 2023, and it will make ICI the first operational sensor observing Earth using sub-millimeter(sub-mm) wavelengths. The main objective of ICI is to use high frequency channels for measuring ice cloud properties and improve the representation of ice clouds in regional and global Numerical Weather Prediction(NWP) models. ICI is a conically scanning radiometer that will measure 13 frequencies from 183\,GHz up to 664\, GHz.  Among all available channels, 183.31\,GHz, 325.15\,GHz and 448.00\,GHz, will measure vertical polarization;  while other channels around frequencies 243.20\,GHz and 664.00\,GHz are ``window channels'' and will measure both vertical and horizontal polarization. The instrument will observe earth from a mean altitude of 832\,Km with sensor viewing angle 44.767$^\circ$(measured from nadir). For all the channels, the mean footprint size is about 15\,Km, but the exact geo-location of samples differs. Therefore a simultaneous utilization of data from different channels shall require remapping to a common footprint \citep{eriksson:towar:20}.

@@

\subsection{Simulations}
%
MWHS-2 simulated radiances are routinely calculated at ECMWF for their use in the ECMWF NWP system. RTTOV and RTTOV-SCATT are used to calculate the radiances in clear-sky and all-sky conditions, respectively. For this study, MWHS-2 brightness temperatures for the period June-July 2020 are used. Out of all the available observations, we use data for latitudinal range $60^{\degree}$\,S to $60^{\degree}$\,N and satellite zenith angle less than $7.5^{\degree}$. With this filter we have 340\,000 cases for each frequency.

ICI and AWS frequencies are simulated with ARTS. Cloudsat profiles during August 2015 are randomly selected for forward simulations. The input data are restricted between $60^{\degree}$S to $60^{\degree}$N, and surface is below 500\,m. Both clear-sky and all-sky scenarios  are simulated. The complete simulation setup is described in Appendix \ref{appendix:ARTS_setup}. For each ICI frequency in Table~\ref{tab:ICI_MWI_channels}, 220\,000 cases are simulated. All ICI frequencies are simulated directly. For AWS, 140\,000 cases are simulated. Forward simulations are performed for 21 monochromatic frequencies, and later these frequencies are interpolated to a finer grid to get the AWS channel brightness temperatures. All AWS sensor viewing angles (from $0^\circ$ to $45^\circ$) are simulated, but the results described in this study are based on nadir viewing angle. Simulations for all three sensors are noise free, so to incorporate the measurement uncertainties, whenever needed, gaussian noise is added to according to the channel NE$\Delta$T (Table~\ref{tab:specifications_MWHS2} - Table~\ref{tab:specifications_AWS}).

The noise free simulations are split into training and testing datasets. The training dataset is used to train the machine learning model, while the testing dataset is used to evaluate the trained model. The construction and details of the model are described in Sect.~\ref{sec:QRNN}. For MWHS-2, 220\,000 simulations are randomly selected as training dataset, while 70\,000 were used for testing. For ICI, 175\,000 cases are randomly picked to form the training set. The remaining 45\,000 are used for testing. A smaller database is selected for AWS. 120\,000 simulations are used for training and the rest are used for testing.

@@

For this application, the predicted percentiles are chosen to be
$0.2\%, 3\%, 16\%, 50\%, 85\%, 97\%$ and $99.8\%$. For a Gaussian
distribution with mean $\mu$ and standard deviation $\sigma$, the quantiles
approximately correspond to $\mu -3\sigma, \mu-2\sigma, \mu-\sigma
, \mu, \mu + \sigma, \mu + 2\sigma, \mu + 3\sigma$ and thus allows
estimation of the $\pm 1, \pm 2$ and $\pm 3\sigma$ confidence intervals.

QRNN's are trained to minimize the mean of the quantile loss functions
%
\begin{align}
  \mathcal{L}_\tau(y_\tau, y) &=
  \begin{cases}
    \tau|y - y_\tau|, & y_\tau < y \\ (1 - \tau)|y_\tau - y|, & \text{otherwise}
    \\
  \end{cases}
\end{align}
%
for all predicted quantile fractions $\tau$, where $\y_\tau$ is the predicted
quantile and $y$ the reference value from the training set. The quantile loss is
used in this study as a performance criterion for the tuning of the hyper
parameters of the QRNN (see Appendix~\ref{appendix:hyperparamter}). In addition to the quantile loss, also the Continuously
Ranked Probability Score (CRPS) is considered. Given a predicted cumulative
distribution function (CDF) $F$ and the reference value $y$, the CRPS is defined as
%
\begin{align}
  \text{CRPS}(F, y) = \int_{-\infty}^{\infty} \left (F(y') - y\right )^2\: dy'.
\end{align}
%
To compute the CRPS for a predictions from a QRNN, the predicted quantiles are
used to derive a piece-wise linear approximation of the CDF of the predicted
distribution and evaluate the above integral.

The implementation of QRNN is similar to one described in \citet{pfreundschuh:aneur:18}, except that instead of Keras python package, PyTorch, an open source machine learning
library \citep{paszke2017automatic} is used. This version is developed and available as a part of \textit{typhon:tools for atmospheric research} software package [\todo{developer's version??}]. The major challenge for implementing QRNN for the current application was to select high performing neural network architecture. This was obtained through grid search over different hyperparameter configurations. The details are described in Appendix~\ref{appendix:hyperparamter}

\subsubsection{QRNN model configurations}
%
\label{sec:QRNN_configuration}
In the study, two QRNN configurations are formulated for cloud-correction. The basic construction of both is to individually train for each of the available 183\,GHz channels, using certain input training data. The input data is all-sky brightness temperatures from selected input channels and/or additional data like land/sea mask. The output in both configurations is NFCS value for the target 183\,GHz channel. The two configurations differ only by the number of input 183\,GHz channels used in the training process:

\begin{enumerate}
	\item QRNN-single: In this configuration, the training input includes all-sky brightness temperatures from the target 183\,GHz channel and other non-humidity channels. Additional data is included, if relevant. No other 183\,GHz channel is included.

@@

For all three sensors described in this study, one or both of the above QRNN configurations are used. The selection of input channels is sensor dependent and is described in detail when introduced.

\subsection{Evaluation metrics}
\label{sec:validation}
\begin{figure}[t]
	\centering
	\includegraphics[height=45mm]{Figures/posterior_distribution_I1V.pdf} 
	\caption{An example showing the predicted quantiles of the conditional distribution of $\ynfcs$ }
	\label{fig:posterior_distribution_I1V}	
\end{figure}
QRNN predictions are posterior probability distribution of the NFCS values described over the chosen quantiles. In order to facilitate the interpretation of results, an example QRNN output is shown in Fig.~\ref{fig:posterior_distribution_I1V}. This example illustrates the predicted quantiles for three different cases. This is in contrast with other conventional correction/filtering methods, which give out only point estimates. However, for most analysis, usually a single point estimate is required. In Bayesian analysis, usually the posterior mean or posterior median are selected as point estimates. In this study, we assume the posterior median to be the best estimate for the predicted NFCS value ($\ynfcs$). To analyse the ability of QRNN in correctly predicting the point estimate, deviation of the median value from the corresponding true value ($\yonfcs$) is evaluated using common performance indicators like bias, mean absolute error(MAE) and standard deviation (STD). The asymmetry of error distributions around their mean is also calculated through the measure of skewness. For a univariate dataset of length $N$, the Fisher-Pearson coefficient of skewness is defined as: 
\begin{equation}
g_1 = 	\frac{\sqrt{N(N-1)}}{N-2} \frac{\sum_{i = 1}^{N}(Y_i - \bar{Y})^3/N}{\sigma^3}
\end{equation}
where $\bar{Y}$ and $\sigma$ are mean and standard deviation of the dataset, respectively.

For probabilistic predictions, accuracy of the point estimate is inadequate to gauge the complete performance. In a successful QRNN training, QRNN learns to predict not only an accurate point estimate but also the correct underlying uncertainty. An ideal QRNN output should be sharp or in other words, all predicted quantiles should be concentrated in the vicinity of the point estimate. The predicted posterior distribution should also be well calibrated, that is, reflect the a priori probability distribution. A straightforward way to compare the two distributions is to plot the frequency of predictions and frequency of the true value in different prediction intervals. This is also commonly known as calibration plot. In a well-calibrated QRNN model, the calibration plot should follow the straight line y = x. Another way to assess how well the predicted posterior distribution reflects the observed errors is to compare the predicted and observed errors. The predicted error is deviation of a random sample drawn from the posterior distribution to its median. In this study, we analyse both calibration plot and predicted errors to assess the correctness of predicted uncertainties.

@@

\section{Correcting cloud affected data in MWHS-2}
%
In this section, we introduce the QRNN based cloud  correction in the context of current operational sensors.  We use MWHS-2 to demonstrate the results. The choice is motivated by the fact that MWHS-2 has five complementary 183\,GHz channels as ATMS/MWS, along with additional 118\,GHz channel. In order to formulate and test the correction approach, multiple QRNN experiments are performed for MWHS-2 channel 14. Later the methodology is expanded to other 183\,GHz channels. A brief comparison of the results is also made against existing cloud filtering methods. Further, the estimates of case-specific uncertainties obtained from QRNN are also evaluated.

\subsection{Experiments}
%
For MWHS-2, multiple experiments using both QRNN configurations are performed. With different experiments we aim to delve into the sensitivity of the method to different input channels:

@@

	\item In the first experiment, we examine the performance of QRNN cloud correction with MWHS-2 window channels: 89 and 150\,GHz. In ECMWF NWP system, the differences between the observations of these two window channels (Scattering Index) \citep{Lu2015FY3C} are used to identify the cloud affected data for ATMS, MHS and MWHS-2. To investigate the potential impact of these two window channels in QRNN based cloud correction, the configuration QRNN-single is applied to predict cloud free radiances. In this experiment, the training input includes all-sky brightness temperatures from target 183\,GHz channel, 89\,GHz and 150\,GHz. Both 89 and 150\,GHz are window channels so the land sea mask is also included as a training input. For example, for channel 14, the training inputs are all-sky brightness temperatures from channels 14, 1, 10 and land/sea mask. This combination is referred as 89+150\,GHz in the text.

@@

	\item The third experiment is designed to assess the exclusive impact of 150\,GHz in cloud correction. This experiment is motivated by the fact that hydrometeor impact at 150\,GHz is stronger as compared to 89\,GHz, and is less affected by surface emissivity. In this experiment, QRNN-single is trained with brightness temperatures from 150\,GHz along with the target channel and land/sea mask.

	\item The fourth experiment is based on the configuration QRNN-all. In this experiment, we use 89 and 150\,GHz channels along with all 183\,GHz channels to train QRNN. The use of 183\,GHz channels for ``self'' cloud filtering has been studied by  \citet{buehler:aclou:07}. They show that brightness temperatures between outer and inner humidity channels can be used as a criterion for cloud filtering. With QRNN-all, we investigate if additional humidity channels in the training process can improve the performance. It should be noted that though the training inputs are same for each 183\,GHz channel, the output is the target 183\,GHz channel; thus each channel still needs to be trained separately. Land/sea mask is also included in the training. This combination is denoted as 89+150+183\,GHz
\end{enumerate}

@@

\subsubsection{QRNN-single applied to MWHS-2 channel 14} 
\begin{figure}[t]
	\centering
	\includegraphics[height=55mm]{Figures/QRNN_output_mwhs.pdf} 
	\caption{Distribution of point estimate $\ynfcs$ obtained from QRNN-single 89+150\,GHz for MWHS-2 channel 14. The corresponding distributions for all-sky and clear-sky simulations are also shown.}
	\label{fig:distribution_predicted_mwhs14}	
\end{figure}
\begin{table*}[t]
	\caption{Error statistics for deviations of NFCS predictions to simulations. Results are for different QRNN experiments for MWHS-2 channel 14. The results from input channel combinations 89+150\,GHz, 89+150+118\,GHz and 150\,GHz are with QRNN-single. While with QRNN-all, only combination 89+150+183\,GHz is shown. The statistics for uncorrected all-sky simulations and NFCS simulations are also provided. The label ``All'' refers to entire predicted dataset, while Filtered(5\,K) denotes the subset where predictions with correction greater than 5\,K are omitted. The fraction of rejected cases is given in parentheses. }
	\label{tab:error_statistics_mwhs_14}
	\begin{tabular}{lrr|rr|rr|rr|rr}
		\tophline
		&\multicolumn{2}{c|}{Simulations}& \multicolumn{6}{c|}{QRNN-single} & \multicolumn{2}{c}{QRNN-all}\\
		\cline{2-11}
		%		\hline
		&   Clear-sky &   All-sky &  \multicolumn{2}{c|}{89+150\,GHz} & \multicolumn{2}{c|}{89+150+118\,GHz} & \multicolumn{2}{c|}{150\,GHz} & \multicolumn{2}{c}{89+150+183\,GHz}\\
		&			   &			& All & Filtered(5K) & All & Filtered(5K) & All & Filtered(5K)  & All & Filtered(5K)\\
		\middlehline
		bias     &  0.00 &  -0.84 & -0.09 & -0.08(3.3\%) & -0.04 & -0.03(3.4\%) & -0.09 & -0.09(3.2\%) & -0.09(3.3\%) & -0.08(3.3\%)  \\
		mae      &  0.80 &   1.45 &  0.88 &  0.86 &  0.89 &  0.87 &  0.89 &  0.87 &  0.62 &  0.59\\
		std      &  1.00 &   3.90 &  1.19 &  1.14 &  1.19 &  1.15 &  1.21 &  1.16 &  0.90 &  0.83\\
		skewness & -0.00 & -14.34 & -1.11 & -0.93 & -1.00 & -0.84 & -0.88 & -0.98 & -1.58 & -1.62\\
		\bottomhline
	\end{tabular}
\end{table*}

Fig.~\ref{fig:distribution_predicted_mwhs14} shows the distribution of QRNN predictions obtained from QRNN. The predicted values are able to remove most of the low brightness temperature cases, and overall a good match with the NFCS simulations is observed. QRNN is unable to predict the lowest clear-sky brightness temperatures, and cases with brightness temperatures around 260\,K occur frequently. The corresponding error statistics(Sect.~\ref{sec:validation}) are displayed in  Table~\ref{tab:error_statistics_mwhs_14}. In the uncorrected data, cloud impact causes a large negative skewness(-14.34) in the error distribution and the corresponding bias is -0.84\,K. Training QRNN with 89 and 150\,GHz removes a part of the cloud impact and reduces the bias to -0.09\,K, and the skewness is -1.11. The MAE and STD are also reduced. Including 118\,GHz in the training, gives comparable results as 89+150\,GHz. With 118\,GHz, the error distributions have lower bias and are more symmetric, but the MAE and STD remain unaltered. This indicates that the information from 118\,GHz channels can be beneficial in predicting few cases correctly, but the overall consequence is not exceptionally different from 89+150\,GHz. Similar is the case with using only 150\,GHz. In the latter, predictions have the most symmetric  error distributions, but the highest spread.
